Title

### 2023-07-31 main_plos_tmp.tex
Cambios

\linenumbers

@@

\begin{figure}[!h] % {{{
\centering
%\includegraphics{images/circuito_general.pdf}
\caption{{\bf Circuit for an $N$-qubit
Pauli channel.}
The circuit creates the state $\sum_{\vec{\gamma}} b_{\vec{\gamma}}|\vec{\gamma}\rangle$ 
on the $2N$ ancilla qubits denoted by $\tilde{q}$.}
\label{Fig1}
\end{figure} % }}}

@@

For the particular case of a Pauli channel on one qubit, the circuit that
simulates it can be constructed as in \fref{Fig2},
which is a special case of \fref{Fig1}
but with all details  explicitly shown.
In said figure, the ancilla state
of \eref{eq: state} can be taken to be
$\sqrt{k_{00}} |00\rangle + \sqrt{k_{01}} |01\rangle + \sqrt{k_{10}} 
|10\rangle + \sqrt{k_{11}}|11\rangle$
and it is created on the ancilla qubits with the help of three rotations of angles
defined by the following equations:
\begin{align}
\label{eq:angle}
\cos\left(\dfrac{\theta_0}{2} \right) &= \sqrt{k_{00} + k_{01}},\nonumber \\
\tan\left( \dfrac{\theta_1 + \theta_2}{2} \right) &= \sqrt{k_{01}/k_{00}},  \\
\tan\left( \dfrac{\theta_2 - \theta_1}{2} \right) &= \sqrt{k_{11}/k_{10}}.  \nonumber
\end{align}

\begin{figure}[!h] % {{{
\centering
%\includegraphics{images/circuito_unqubit.pdf}
\caption{
{\bf One-qubit Pauli channel circuit.} Circuit for a one-qubit Pauli channel,
which is a particular case of \fref{Fig1}.  Here we have two
ancilla qubits and we use three rotations
of angles given by \eref{eq:angle} to create the Ancilla State of
of \eref{eq: state} for the two ancilla qubits.
}
\label{Fig2} 
\end{figure} % }}}

@@

\begin{figure}[!h] % {{{
\centering
\caption{{\bf Results of the diamond fidelities as defined in \eref{eq:diamond-fid}
for a sample of Pauli channels in the tetrahedron.}  Notice that channels close
to the center of the tetrahedron have high fidelities, while those close to the
borders do not.  Moreover, we show the results for cuts of the tetrahedron at
different values of $\tau_3$.}
\label{Fig3}
\end{figure} % }}}

@@

\begin{figure}[!h] % {{{
\centering
%\includegraphics{images/OPR-circuit.pdf}
\caption{\textbf{General form of a 1PR circuit}.
Any 1PR circuit can be transformed into this form,
where the rotation on the last qubit
can be controlled or not by any of the other qubits.
$A$ and $B$
are $N$-qubit gates that do not depend on the parameter $p$ and
$s= s(p)$ is a function of the parameter.
}
\label{Fig4}
\end{figure} % }}}

@@

\begin{figure}[!h] % {{{
%\captionsetup[subfigure]{justification=centering}
\centering
%\begin{subfigure}{.45\textwidth}
%  \centering
%  \includegraphics[width=.9\linewidth]{images/curvas.png}
%   \caption{}
%  \label{Fig51}
%\end{subfigure}%
%\begin{subfigure}{.45\textwidth}
%  \centering
%  \includegraphics[width=.9\linewidth]{images/curvas-azar.png}
%  \caption{}
%  \label{Fig5-2}
%\end{subfigure}
\caption{{\bf Some Pauli dynamical maps that can be implemented with a 1PR circuit.}
The curves painted in these tetrahedrons
represent Pauli dynamical maps that can be implemented with 1PR circuits.
(a) shows the dynamical maps mentioned in the main 
text, which are: depolarizing (purple), bit flip (blue),
phase flip (green), bit-phase flip (red)
and parabolic (orange).
(b) shows dynamical maps selected at random that can be implemented with 1PR 
circuits.}
\label{Fig5}
\end{figure} % }}}

@@

% }}}
%\section{Supporting information} % {{{

% Include only the SI item label in the paragraph heading. Use the \nameref{label} command to cite SI items in the text.
% \paragraph*{S1 Fig.}
% \label{S1_Fig}
% {\bf Bold the title sentence.} Add descriptive text after the title of the item (optional).
% 
% \paragraph*{S2 Fig.}
% \label{S2_Fig}
% {\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
% 
% \paragraph*{S1 File.}
% \label{S1_File}
% {\bf Lorem ipsum.}  Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
% 
% \paragraph*{S1 Video.}
% \label{S1_Video}
% {\bf Lorem ipsum.}  Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
% 
% \paragraph*{S1 Appendix.}
% \label{S1_Appendix}
% {\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
% 
% \paragraph*{S1 Table.}
% \label{S1_Table}
% {\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
% }}}
\section{Acknowledgments} % {{{
Support by projects CONACyT 285754, and UNAM-PAPIIT IG101421 is acknowledged.

% Either type in your references using
% \begin{thebibliography}{}
% \bibitem{}
% Text
% \end{thebibliography}
%
% or
%
% Compile your BiBTeX database using our plos2015.bst
% style file and paste the contents of your .bbl file
% here. See http://journals.plos.org/plosone/s/latex for 
% step-by-step instructions.

@@

\bibitem{Andrea}
Far\'ias OJ, Aguilar GH, Vald\'es-Hern\'andez A, Ribeiro PHS, Davidovich L,
  Walborn SP.
\newblock Observation of the emergence of multipartite entanglement between a
  bipartite system and its environment.
\newblock Phys Rev Lett. 2012;109(15):150403.

@@

\bibitem{Flammia}
Steven F, Joel W.
\newblock Efficient estimation of Pauli channels.
\newblock ACM. 2020;1(3):1--32.

@@

\bibitem{jamil}
Jamiołkowski A.
\newblock Linear transformations which preserve trace and positive
  semidefiniteness of operators.
\newblock Rep Math Phys. 1972;3(4):275--278.

@@

\bibitem{Andrea_4qb}
Aguilar GH, Far\'ias OJ, Vald\'es-Hern\'andez A, Souto~Ribeiro PH,
  Davidovich L, Walborn SP.
\newblock Flow of quantum correlations from a two-qubit system to its
  environment.
\newblock Phys Rev A. 2014;89(2):022339.

@@

% }}}
\appendix
\end{document}

>>>>

@@

\begin{figure} % {{{
\centering
\caption{{\bf Circuit for an $N$-qubit
Pauli channel.}
The circuit creates the state $\sum_{\vec{\gamma}} b_{\vec{\gamma}}|\vec{\gamma}\rangle$ 
on the $2N$ ancilla qubits denoted by $\tilde{q}$.}
\label{Fig1}
\end{figure} % }}}

@@

For the particular case of a Pauli channel on one qubit, the circuit that
simulates it can be constructed as in \fref{Fig2},
which is a special case of \fref{Fig1}
but with all details  explicitly shown.
In said figure, the ancilla state
of \eref{eq: state} can be taken to be
$\sqrt{k_{0}} |00\rangle + \sqrt{k_{1}} |01\rangle + \sqrt{k_{2}} 
|10\rangle + \sqrt{k_{3}}|11\rangle$
and it is created on the ancilla qubits with the help of three rotations of angles
defined by the following equations:
\begin{align}
\label{eq:angle}
\cos\left(\dfrac{\theta_0}{2} \right) &= \sqrt{k_{0} + k_{1}},\nonumber \\
\tan\left( \dfrac{\theta_1 + \theta_2}{2} \right) &= \sqrt{k_{1}/k_{0}},  \\
\tan\left( \dfrac{\theta_2 - \theta_1}{2} \right) &= \sqrt{k_{3}/k_{2}}.  \nonumber
\end{align}

\begin{figure} % {{{
\centering
\caption{
{\bf One-qubit Pauli channel circuit.} Circuit for a one-qubit Pauli channel,
which is a particular case of \fref{Fig1}.  Here we have two
ancilla qubits and we use three rotations
of angles given by \eref{eq:angle} to create the Ancilla State of
of \eref{eq: state} for the two ancilla qubits.
}
\label{Fig2} 
\end{figure} % }}}

@@

\begin{figure} % {{{
\centering
\caption{{\bf Results of the diamond fidelities as defined in \eref{eq:diamond-fid}
for a sample of Pauli channels in the tetrahedron.}  Notice that channels close
to the center of the tetrahedron have high fidelities, while those close to the
borders do not.  Moreover, we show the results for cuts of the tetrahedron at
different values of $\tau_3$.}
\label{Fig3}
\end{figure} % }}}

@@

\begin{figure} % {{{
\centering
\caption{\textbf{General form of a 1PR circuit}.
Any 1PR circuit can be transformed into this form,
where the rotation on the last qubit
can be controlled or not by any of the other qubits.
$A$ and $B$
are $N$-qubit gates that do not depend on the parameter $p$ and
$s= s(p)$ is a function of the parameter.}
\label{Fig4}
\end{figure} % }}}

@@

\begin{figure} % {{{
\centering
\caption{{\bf Some Pauli dynamical maps that can be implemented with a 1PR circuit.}
The curves painted in these tetrahedrons
represent Pauli dynamical maps that can be implemented with 1PR circuits.
(a) shows the dynamical maps mentioned in the main 
text, which are: depolarizing (purple), bit flip (blue),
phase flip (green), bit-phase flip (red)
and parabolic (orange).
(b) shows dynamical maps selected at random that can be implemented with 1PR 
circuits.}
\label{Fig5}
\end{figure} % }}}

@@

% }}}
\section{Supporting information} % {{{

% Include only the SI item label in the paragraph heading. Use the \nameref{label} command to cite SI items in the text.
\paragraph*{S1 Code.}
 \label{S1_code}
 {\bf Simulation of Pauli Channels.} Python code for the simulation of Pauli channels on IBM's quantum computers.
% \paragraph*{S2 Fig.}
% \label{S2_Fig}
% {\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
% 
% \paragraph*{S1 File.}
% \label{S1_File}
% {\bf Lorem ipsum.}  Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
% 
% \paragraph*{S1 Video.}
% \label{S1_Video}
% {\bf Lorem ipsum.}  Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
% 
% \paragraph*{S1 Appendix.}
% \label{S1_Appendix}
% {\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
% 
% \paragraph*{S1 Table.}
% \label{S1_Table}
% {\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
% }}}

\section{Acknowledgments} % {{{
Support by projects CONACyT 285754, and UNAM-PAPIIT IG101421 is acknowledged.

% Either type in your references using
% \begin{thebibliography}{}
% \bibitem{}
% Text
% \end{thebibliography}
%
% or
%
% Compile your BiBTeX database using our plos2015.bst
% style file and paste the contents of your .bbl file
% here. See http://journals.plos.org/plosone/s/latex for 
% step-by-step instructions.
% }}}

@@

\bibitem{Andrea}
Far\'{\i}as OJ, Aguilar GH, Vald\'es-Hern\'andez A, Ribeiro PHS, Davidovich L,
  Walborn SP.
\newblock Observation of the emergence of multipartite entanglement between a
  bipartite system and its environment.
\newblock Phys Rev Lett. 2012;109(15):150403.

@@

\bibitem{Flammia}
Flammia S, Wallman J.
\newblock Efficient estimation of Pauli channels.
\newblock ACM Transactions on Quantum Computing. 2020;1(3):1--32.

@@

\bibitem{jamil}
JamioÅ‚kowski A.
\newblock Linear transformations which preserve trace and positive
  semidefiniteness of operators.
\newblock Rep Math Phys. 1972;3(4):275--278.

@@

\bibitem{Andrea_4qb}
Aguilar GH, Far\'{\i}as OJ, Vald\'es-Hern\'andez A, Souto~Ribeiro PH,
  Davidovich L, Walborn SP.
\newblock Flow of quantum correlations from a two-qubit system to its
  environment.
\newblock Phys Rev A. 2014;89(2):022339.

@@

\end{document}
